---
title: "Assignment 2 - Making a Simple Plot"
Author: "Ryan Rodriguez"
Date: "February 17,2021"
output: html_notebook
---

#Import the library packages that I need
```{r}
library(readr)
library(ggplot2)
```

#Read the dataset into R Studio
```{r}
df_enrollment <- read.csv('enrollment.csv')

```

#View the dataset's column names and its data type
```{r}
glimpse(df_enrollment)
```

#A quick mathematical summary of the dataset
```{r}
summary(df_enrollment)
```

#View how many rows in this dataset
```{r}
nrow(df_enrollment)
```

#Verfiying that there is no NA values in the dataset
```{r}
is.na(df_enrollment)
```

#Viewing all the year values
```{r}
df_enrollment$year
```

#Slicing the year columns to gather data from the last decade of enrollment
```{r}
df_2010s_enrollment <- slice(df_enrollment, (3:12))
```


#Plot the data on the number of enrollment based on the last decade.
#Used the sliced dataset "df_2010s_enrollment" as the data
#Used "year" as the x variable and the "total" is the y variable
#Used the point graph to visualize the data
#Used labs to give the graph the title, X, and Y axis label
#Used theme to adjust the x and y tick marks, lowering the text size and angle to remove the clustering view of the years overlapping each other.
```{r}
ggplot(data=df_2010s_enrollment, aes(x=year, y=total)) +
  geom_point() +
  labs(title = 'Stockton Enrollment in 2010s', x = 'Year', y = '# of Enrollment') +
  theme(axis.text.x = element_text(size=8, angle=45),
          axis.text.y = element_text(size=8, angle=45))
```
